### 2025-06-17 index.qmd
20250617 - SimDesign

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "downlit", "xml2",
  "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", "gsisdecoder", 
  "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", "dagitty", 
  "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "bbmle", "fitdistrplus", "mclust", "magrittr", 
  "viridis", "plotly", "quantmod", "fPortfolio", "xts", "zoo", "forecast", #"webshot2", 
  "stringi", "parallel", "parallelly", "doParallel", "missRanger", "ggridges", 
  "powerjoin", "caret", "gpboost", "cmdstanr", "learnr", "remotes", "corrplot", 
  "correlation", "mgcv", "rms", "car", "performance", "lavaan", "mice", 
  "miceadds", "interactions", "shiny", "PearsonDS", "robustbase", "data.table", 
  "future", "future.apply"
)

>>>>

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "downlit", "xml2",
  "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", "gsisdecoder", 
  "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", "dagitty", 
  "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "bbmle", "fitdistrplus", "mclust", "magrittr", 
  "viridis", "plotly", "quantmod", "fPortfolio", "xts", "zoo", "forecast", #"webshot2", 
  "stringi", "parallel", "parallelly", "doParallel", "missRanger", "ggridges", 
  "powerjoin", "caret", "gpboost", "cmdstanr", "learnr", "remotes", "corrplot", 
  "correlation", "mgcv", "rms", "car", "performance", "lavaan", "mice", 
  "miceadds", "interactions", "shiny", "PearsonDS", "robustbase", "data.table", 
  "future", "future.apply", "SimDesign"
)

### 2025-06-17 simulation.qmd
20250617 - SimDesign

```{r}
library("ffanalytics")
library("data.table")
library("future")
library("future.apply")
library("progressr")
library("tidyverse")
```

@@

>>>>

```{r}
library("ffanalytics")
library("data.table")
library("future")
library("future.apply")
library("progressr")
library("SimDesign")
library("tidyverse")
```

@@

You can generate a template for Monte Carlo simulations in the `SimDesign` package using the following code:

```{r}
SimDesign::SimFunctions()
```

#-------------------------------------------------------------------

Design <- SimDesign::createDesign(
  factor1 = NA,
  factor2 = NA)

#-------------------------------------------------------------------

Generate <- function(condition, fixed_objects) {
  dat <- data.frame()
  dat
}

Analyse <- function(condition, dat, fixed_objects) {
  ret <- nc(stat1 = NaN, stat2 = NaN)
  ret
}

Summarise <- function(condition, results, fixed_objects) {
  ret <- c(bias = NaN, RMSE = NaN)
  ret
}

#-------------------------------------------------------------------

res <- SimDesign::runSimulation(
  design = Design,
  replications = 2,
  generate = Generate,
  analyse = Analyse,
  summarise = Summarise)

res
```
